### 2022-01-15 cleave.tex
final fixes

Implementation-wise, \ac{CLEAVE} is built on top of the well-established and stable \emph{Twisted}\footnote{\url{https://twistedmatrix.com}} asynchronous programming and networking framework.
The aforementioned core components (\emph{State}, \emph{Controller}, \emph{Sensors}, and \emph{Actuators}) are provided as abstract base classes with core functionality that users need to extend for their specific use case and \ac{NCS}.
On the other hand, the framework handles network communication and metric collection autonomously; users only need to select the desired transport protocol (we do however provide an \ac{API} for extending the available transports).

@@

Once the core components for the emulation have been defined and implemented, they need to be registered with the framework.
This is done through Python scripts which simply define a number of required (and some optional) top-level variables, corresponding to emulation parameters such as the \emph{State}, \emph{Controller}, \emph{Sensor}, and \emph{Actuator} subclasses to use; the emulation update rate; the controller side host and address; data output directories; and so on.
These Python configuration files are then provided as arguments to the \texttt{cleave} command line provided by the framework.
\ac{CLEAVE} imports and parses them, and then sets up and executes the emulation.

>>>>

Implementation-wise, \ac{CLEAVE} is built on top of the well-established and stable \emph{Twisted}\footnote{\url{https://twistedmatrix.com}} asynchronous programming and networking framework.
The aforementioned core components (\emph{State}, \emph{Controller}, \emph{Sensors}, and \emph{Actuators}) are provided as abstract base classes with core functionality that users must extend for their specific use cases and \acp{NCS}.
On the other hand, the framework handles network communication and metric collection autonomously; users only need to select the desired transport protocol (we do however provide an \ac{API} for extending the available transports).

@@

Once the core components for the emulation have been defined and implemented, they need to be registered with the framework.
This is done through Python scripts which simply define a number of required (and some optional) top-level variables, corresponding to emulation parameters such as the \emph{State}, \emph{Controller}, \emph{Sensor}, and \emph{Actuator} subclasses to use; the emulation update rate; the controller-side host and address; data output directories; \emph{et cetera}.
These Python configuration files are then provided as arguments to the \texttt{cleave} command line provided by the framework.
\ac{CLEAVE} imports and parses them, and then sets up and executes the emulation.

### 2022-01-15 conclusion.tex
final fixes

There is still, however, work to be done.
The current implementation only includes a single plant-controller pair; we envision creating an open library of \acp{NCS} to share with the community.
At the moment, the interactions of \ac{CLEAVE} and tools such as Docker are still quite superficial.
Our goal is to achieve a much tighter integration, e.g.\ by providing the toolkit as pre-packaged container images.
Finally, the validity of the results obtained by the framework will have to be verified through more thorough, realistic scenarios than what we have been able to show in this work.
In particular, we intend to perform large-scale experimentation targetting 5G cellular deployments, as this technology is set to become the backbone of edge networks in the near future.

>>>>

There is still, however, work to be done.
We are extending the number of plant and controller implementations on the framework, with the goal of creating an open library of \acp{NCS} to share with the community.
At the moment, the interactions of \ac{CLEAVE} and tools such as Docker are still quite superficial.
Our goal is to achieve a much tighter integration, e.g.\ by providing the toolkit as pre-packaged container images.
Finally, the validity of the results obtained by the framework will have to be verified through more thorough, realistic scenarios than what we have been able to show in this work.
In particular, we intend to perform large-scale experimentation targetting 5G cellular deployments, as this technology is set to become the backbone of edge networks in the near future.

### 2022-01-15 experiments.tex
final fixes

As expected, higher sampling rates directly correlate to better quality of control (with the exception of the \SIlist{40;60}{\hertz}, \SI{50}{\milli\second} scenarios --- we attribute this to randomness and the relatively short duration of the experiments).
As sampling rates increased, the system was able to reach stability at higher \acp{RTT}.
These initial results already hint at interesting consequences for \ac{NCS} deployments on the edge.
For instance, it is clear from \cref{fig:single:stability} that network delays can, to a certain extent, be compensated for by increasing the sampling rate of the system.
A corollary of this is, conversely, that at lower network latencies \acp{NCS} are able to stabilize at lower sampling rates.
Adaptive sampling might thus be a viable method for optimizing \ac{NCS} resource utilization at the edge.

>>>>

As expected, higher sampling rates tend to correlate with better quality of control; at higher sampling rates the system was able to reach stability at higher \acp{RTT}.
These initial results already hint at interesting consequences for \ac{NCS} deployments on the edge.
For instance, it is clear from \cref{fig:single:stability} that network delays can, to a certain extent, be compensated for by increasing the sampling rate of the system.
A corollary of this is, conversely, that at lower network latencies \acp{NCS} are able to stabilize at lower sampling rates.
Adaptive sampling might thus be a viable method for optimizing \ac{NCS} resource utilization at the edge.

### 2022-01-15 intro.tex
final fixes

In this paper, we present the first fully-software-based framework for scalable and repeatable benchmarking of edge-native \ac{NCS}.
As the edge computing paradigm starts to be adopted by industry, more and more variations of it have started to appear in literature.
``Near'', ``far'', ``core'', and ``telco'' edge, among others, are all terms which describe variations of the original concept and which are becoming ubiquitous in new research.
While the core idea of edge computing is widely accepted as fundamental for pervasive \acp{NCS} in general, understanding the strenghts and weaknesses of such different edge concepts is of paramount importance.

@@

The rest of this paper is structured as follows.
\cref{sec:approach} presents the design principles of the framework.
In \cref{sec:experiments}, we present a series of experiments which validate the utility, flexibility, and repeatability of \ac{CLEAVE}.
Finally, in \cref{sec:conclusion} we conclude this paper and briefly discuss future work.

>>>>

In this paper, we present the first fully-software-based framework for scalable and repeatable benchmarking of edge-native \ac{NCS}.
As the edge computing paradigm starts to be adopted by industry, more and more variations of it have begun to appear in literature.
``Near'', ``far'', ``core'', and ``telco'' edge, among others, are all terms which describe variations of the original concept and which are becoming ubiquitous in new research.
While the core idea of edge computing is widely accepted as fundamental for pervasive \acp{NCS} in general, understanding the strenghts and weaknesses of such different edge concepts is of paramount importance.

@@

The rest of this paper is structured as follows.
\cref{sec:approach} presents the design principles and implementation of the framework.
In \cref{sec:experiments}, we present a series of experiments which validate the utility, flexibility, and repeatability of \ac{CLEAVE}.
Finally, in \cref{sec:conclusion} we conclude this paper and briefly discuss future work.
